%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Daniel} \headerlastnamestyle{Carrillo} \\
	\vspace{2mm}
	{\hspace{0.8cm}\faEnvelope\ danielcarrillocardus@gmail.com}  |  {\faMobile\ (+34) 633376521}  |  {\faMapMarker\ Spain} 
	\newline {\faLink\ \href{https://www.linkedin.com/in/danielcarrillocardus/}{https://www.linkedin.com/in/danielcarrillocardus/}}
\end{center}

\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages:  & {\skill{ C\#, JavaScript, TypeScript, Terraform, SQL, HTML, CSS.}} \\
		Frameworks:  & {\skill{ .NET, Vue.js, Node.js, Cypress.js}} \\
		Databases:  & {\skill{ DynamoDB, ElasticSearch/OpenSearch, PostgreSQL.}} \\
		Technologies / Tools: \hspace{0.05cm} & {\skill{ AWS, Lambda, Step Functions, REST, gRPC, npm, Git, GitHub Actions.}} \\
		Practices:  & {\skill{ Agile, Scrum, SOLID Principles, Test-Driven Development, Code Reviews.}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}
\vspace{-7mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Lead Software Developer}
	{Softtek (Royal Society of Chemistry)}
	{Remote, Spain}
	{June 2023 – Present}
	{\begin{cvitems}
		\vspace{0.5mm}
		\item {Designed and launched the new ChemSpider website, a chemical compounds database with  140M+ records, increasing traffic and researcher engagement.}
		\item {Worked on the content distribution pipeline of Pubs, the publishing platform, integrating with PubMed, Google Scholar, and other consumers, expanding the global reach and visibility of RSC publications.}
		\item {Led the migration from on-premise servers to AWS, improving scalability, reliability, and reducing operational costs.}
		\item {Built the Deposition System, streamlining chemical data ingestion and ensuring continuous database growth using AWS Step Functions and Microservices.}
		\item {Reduced infrastructure costs by tens of thousands of pounds annually by migrating from Apigee to a native AWS API Gateway solution.}
		\item {Led a strategic proposal with the client that enabled frontend developers to contribute directly to the expansion of the client\textquotesingle{}s shared component library—enhancing team autonomy and strengthening client collaboration.}
		\item {Responsible for PR reviews, code quality, and mentoring junior developers.}
		\end{cvitems}}

	\cventry
	{Software Developer}
	{Innovation Strategies - A Siemens Company}
	{Palma de Mallorca, Spain}
	{Mar 2021 – June 2023}
	{\begin{cvitems}
		\vspace{0.5mm}
		\item {Led the development of a full stack application that increased room upsell conversion rates, improving overall revenue.}
		\item {Created an innovative 3D room selection tool that enhanced the user experience, allowing customers to visualize and book their exact hotel room, contributing to an increase in booking engagement.}
		\item {Collaborated with cross-functional teams to deliver scalable solutions, ensuring high performance and responsiveness of the booking platform.}
		\item {Ensured high-quality delivery through PR reviews, automated testing, and CI/CD practices.}
		\end{cvitems}}
\end{cventries}

\cvsection{Projects}
\begin{cventries}
	\vspace{-3mm}
	\cventry
	{}
	{Crossbar Challenge \vspace{-5mm}}
	{Unity, C\#, Blender \vspace{-5mm}}
	{}
	{\begin{cvsectionnormaltext}
		\item {Football game with almost 100K downloads in the play store. 
		\newline \faLink\ \href{https://play.google.com/store/apps/details?id=com.DABCStudios.CrossbarChallenge}{https://play.google.com/store/apps/details?id=com.DABCStudios.CrossbarChallenge}}
	\end{cvsectionnormaltext}}

	\vspace{-3mm}
	\cventry
	{}
	{Egg Incubator \vspace{-5mm}}
	{Java, Python, C++ (Qt Framework), Android, Raspberry Pi \vspace{-5mm}}
	{}
	{\begin{cvsectionnormaltext}
		\item{Monitoring and control system for an egg incubator, using a Raspberry Pi. Controlled by an Android app, it is possible to set up the target temperature / humidity and other parameters. Also able to perform manual operations, activating / deactivating the relays to connect lights, resistances, open the door, etc.}
	\end{cvsectionnormaltext}}	
	
	\vspace{-3mm}
	\cventry
	{}
	{Clean Code and SOLID Principles course \vspace{-5mm}}
	{}
	{}
	{\begin{cvsectionnormaltext}
		\item{Published a course on how to write cleaner code.
		\newline \faLink\ \href{https://www.udemy.com/course/principios-solid-y-clean-code-escribe-codigo-de-calidad/}{https://www.udemy.com/course/principios-solid-y-clean-code-escribe-codigo-de-calidad/}}
	\end{cvsectionnormaltext}}
	
	\vspace{-5mm}
	
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{8mm}
\cvsection{Education}
\begin{cventries}
	\vspace{-3mm}
	\cventry
	{}
	{Es Liceu Coop. \vspace{-5mm}}
	{Marratxí, Spain \vspace{-5mm}}
	{2021 \vspace{-5mm}}
	{\begin{cvsectionnormaltext} 
		\item{Higher National Diploma in Web Applications Development or BTEC 5 (Spanish equivalence)}
	\end{cvsectionnormaltext}}
\end{cventries}

\end{document}